Poseidon Adventure

### 2019-05-15 RethinkSamplingFunctions.Rmd
fix typo
stage to age needed

@@

## Proposed solution

@@

1. write an aggregation function for resn and structn that applies the median
2. rewrite `create_survey` to use alternate aggregation functions, or write `create_survey_nums` and `create_survey_wt` functions that use appropriate aggregation
    + the latter may be better, because do we want to apply efficiency and selectivity to median weight densities? I don't think so?
    + the fish still weighs the same, we just don't have the right proportion in the ecosystem (efficiency) or the right proportion at age (selectivty), both of which are taken care of in the numbers. 
    + so maybe `aggregateDensityData` using the standard survey polygons gets us what we need as input to `sample_fish`?
3. rewrite `sample_fish` to use alternate aggregation functions for each input type. Keeping this all in one function makes sense because the functional already takes both numbers and weights as inputs

>>>>

## May 15: True age estimation needs to happen in here

The sequence `create_survey` to `sample_fish` to `calc_age2length` now works. It can go as pictured below if there are not multiple true ages in an age class. Revisions to work on:

1. For clarity, `calc_age2length` should be renamed `calc_stage2length`
2. Between `sample_fish` and `sample_ages` we need the already written `calc_stage2age` function, which calls `calc_Z`. Test these next.
3. Similarly, between `sample_fish` and `sample_weight` we will need to expand to true ages for a weight-at-age vector (for species where stage=age, this is already output as muweight from the `calc_(st)age2length` function).

@@

## Proposed solution (now done for calc_age2length)

@@

1. write an aggregation function for resn and structn that applies the median
    + **Done 10 May, `aggregateDensityData`**
2. rewrite `create_survey` to use alternate aggregation functions, or write `create_survey_nums` and `create_survey_wt` functions that use appropriate aggregation
    + the latter may be better, because do we want to apply efficiency and selectivity to median weight densities? I don't think so?
    + the fish still weighs the same, we just don't have the right proportion in the ecosystem (efficiency) or the right proportion at age (selectivty), both of which are taken care of in the numbers. 
    + so maybe `aggregateDensityData` using the standard survey polygons gets us what we need as input to `sample_fish`?
    + **Yes, did the latter was done**
3. rewrite `sample_fish` to use alternate aggregation functions for each input type. Keeping this all in one function makes sense because the biological sampling already needs both numbers and weights as inputs
    + **Done 10 May, use sample=FALSE option**

### 2019-05-15 docs/index.Rmd
looking for small turbot
stage to age needed

<a href="https://sgaichas.github.io/poseidon-dev/RethinkSamplingFunctions.html" target="_blank">Big picture and new functions needed - May 10, 2019</a>

@@

>>>>

<a href="https://sgaichas.github.io/poseidon-dev/RethinkSamplingFunctions.html" target="_blank">Big picture and new functions needed - May 10, 2019, updated May 15, 2019</a>

@@

Do we see ever small fish for large species? Is this normal, or a problem with length estimation?

<a href="https://sgaichas.github.io/poseidon-dev/TestSmallestLength.html" target="_blank">Should there be small Greenland halibut in NOBA? - May 15, 2019</a>
